---
title: "Crown Institute FTE"
author: "Chris Mellinger"
format: 
  revealjs:
    theme: ftetheme.scss
editor: visual
project:
  type: website
  output-dir: docs
---

## Full Time Equivalent (FTE) {#fte-defined}

```{r}
library(tidyverse)
library(knitr)
library(kableExtra)
```

**FTE**: proportion of a full time work load.

At Crown, a full-time workload is 40 hours per week.

-   Full time: $\frac{40 \text{ hours}}{40\text{ hour work week}} = 1.0 \text{ FTE}$
-   Three-quarters time: $\frac{30 \text{ hours}}{40\text{ hour work week}} = 0.75 \text{ FTE}$
-   Half time: $\frac{20 \text{ hours}}{40\text{ hour work week}} = 0.50 \text{ FTE}$

## Example 1: Lydia {.smaller}

::: columns
::: {.column width="40%"}
Lydia works as a full time worker at Crown and splits her time 40/60 between the finance team and Alma.
:::

::: {.column width="60%"}
```{r}
#| label: lydia-ft

tribble(
  ~`FTE Assigned To`,    ~FTE,   ~`Hours per Week`,   ~`Example Sentence`,
  "Finance team",        0.40,   16,                  "Lydia's FTE assigned to finance is 0.40.",
  "Alma",                0.60,   24,                  "Lydia's Alma-assigned FTE is 0.60",
  "Total",               1.0,    40,                  "Lydia's FTE at Crown is 1.0; she is full time."
) %>% 
  kable() %>% 
  row_spec(3, bold = TRUE, italic = TRUE)
```
:::
:::

## Example 2: Lyle {.smaller}

::: columns
::: {.column width="40%"}
Lyle works for three-quarters of a full time position at Crown. His time is split evenly between the Mind Body Voice (MBV) project and the Mindful Campus project.

::: callout-tip
Percentages and proportions can represent the same number, just with a differently placed decimal:

.50 = 50%
:::
:::

::: {.column width="60%"}
```{r}
#| label: lyle-ft

tribble(
  ~`FTE Assigned To`,    ~FTE,   ~`Hours per Week`,   ~`Example Sentence`,
  "MBV",                 0.375,   15,                  "Lyle's FTE on MBV is 37.5%.",
  "Mindful Campus",      0.375,   15,                  "Lyle's Mindful-Campus-assigned FTE is 0.375",
  "Total",               0.75,    30,                  "Lyle's FTE at Crown is 0.75."
) %>% 
  kable() %>% 
  row_spec(3, bold = TRUE, italic = TRUE)
```
:::
:::

## Example 2: Lyle {.smaller}

Notice, this is *NOT* correct:

> Half of Lyle's FTE is spent on MBV.

Colloquially, we often say: "Half of Lyle's time is on MBV." But when discussing effort, this leads to confusion for people who have more or less than a full time position. Are speaking of half of Lyle's full time work week? Or half of his Crown time? It is not clear with this phrasing.

Rather, this statement is unambiguous with our shared understanding of FTE:

> 37.5% of Lyle's FTE is spent on MBV. He works 75% FTE at Crown.

The definition of FTE is strict; it always answers the question, "how much of a 40 hour work week is dedicated to the purpose?"
